% 中文摘要
\chapter*{\hfill 摘要\hfill}
\phantomsection % Creates a proper hyperlink anchor for hyperref
\addcontentsline{toc}{chapter}{摘要}
統計分析在現代研究中扮演關鍵角色，提供了解析複雜數據集的強大方法論。本論文聚焦於先進統計建模技術的應用，以預測結果並理解大規模數據集中的模式。通過採用回歸分析、貝葉斯推斷及機器學習算法等方法，本研究展示了這些技術在解決數據解析挑戰方面的有效性。研究結果顯示，雖然先進統計模型提升了預測準確性與決策能力，但也凸顯出對假設條件與模型驗證的謹慎需求。本研究為統計學家及研究者提供了提升統計技術應用於多元領域的寶貴見解。

\vspace*{12pt}

\noindent\textbf{關鍵詞：}統計分析、先進統計建模、回歸分析、貝葉斯推斷、機器學習、模型驗證、預測準確性、數據解析 
\clearpage

% 英文摘要
\chapter*{\hfill Abstract\hfill}
\phantomsection % Creates a proper hyperlink anchor for hyperref
\addcontentsline{toc}{chapter}{Abstract}
Statistical analysis plays a critical role in modern research, providing robust methodologies for interpreting complex datasets. This thesis focuses on the application of advanced statistical modeling techniques in predicting outcomes and understanding patterns within large-scale datasets. By employing methods such as regression analysis, Bayesian inference, and machine learning algorithms, the study demonstrates their effectiveness in addressing challenges in data interpretation. The findings reveal that while advanced statistical models improve prediction accuracy and decision-making, they also highlight the need for careful assumptions and model validation. This research offers valuable insights for statisticians and researchers aiming to enhance the application of statistical techniques in diverse fields.

\vspace*{12pt}

\noindent\textbf{Keywords: }Statistical Analysis, Advanced Statistical Modeling, Regression Analysis, Bayesian Inference, Machine Learning, Model Validation, Prediction Accuracy, Data Interpretation
\clearpage
